---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Travis build status](https://travis-ci.org/mdsumner/polymer.svg?branch=master)](https://travis-ci.org/mdsumner/polymer) [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/mdsumner/polymer?branch=master&svg=true)](https://ci.appveyor.com/project/mdsumner/polymer) [![Coverage status](https://codecov.io/gh/mdsumner/polymer/branch/master/graph/badge.svg)](https://codecov.io/github/mdsumner/polymer?branch=master)


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# polymer

The goal of polymer is to provide flexible and intuitive overlay methods
familiar to GIS workflows. This works via finite-element
decomposition of all component edges in all inputs as triangles. Then
triangles *instances* are classified (by point-in-polygon lookup) by inclusion
within paths within objects within layers.

An example. This plot on the left shows 3 overlapping polygon layers, four squares on the bottom, then a single triangle, and then a blue elongated rectangle. The next panel
shows the entire mesh with every input edge included, the purple region has two overlappping polygons, the grey region has three. We can distinguish the various layers by what parts of the plane they occupy, with finite elements that collectively capture the input shapes. 

```{r panels, echo=FALSE}
library(polymer)
par(mfrow = c(1, 2), mar = rep(0, 4))
plot(sf::st_geometry(A), col = viridis::viridis(nrow(A)), reset = FALSE)
plot(sf::st_geometry(B), col = "firebrick", add = TRUE)
plot(sf::st_geometry(C), col = "dodgerblue", add = TRUE)
pool <- polymer(A, B, C)

plot(pool, show_intersection = TRUE)
plot(layer_n(pool, n = 2), add = TRUE, col = "purple")
plot(layer_n(pool, n = 3), add = TRUE, col = "grey70")
```


There are two functions: 

* `polymer()` build the triangle pool from 1 or more input layers
* `layer_n()` extract a simple features layer composed of n-overlaps from the inputs to `polymer()` (default is 2)

There are [print](https://mdsumner.github.io/polymer/reference/print.polymer.html) and [plot](https://mdsumner.github.io/polymer/reference/plot.polymer.html]) methods for the polymer pool. 

We currently ***don't*** keep the input layers linked in the output from `layer_n()` but this will be a key feature in future versions. (You can set an argument to keep them if you are adventurous). We need some intermediate forms because sf itself cannot store multi-relations without duplicating geometries.  

## WIP

* holes are identifiable but not yet explicitly classified
* extend sb_intersection to return the right parts
* write sensible return types and include nput attributes



## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mdsumner/polymer")
```

## Example

This example takes three built in data sets and merges them together as an indexed mesh. 

```{r example}
library(polymer)
plot(sf::st_geometry(A), col = viridis::viridis(nrow(A)))
plot(sf::st_geometry(B), col = "firebrick", add = TRUE)
plot(sf::st_geometry(C), col = "dodgerblue", add = TRUE)

## summarize the contents
(pool <- polymer(A, B, C))

## show the components pieces
plot(pool, asp = 1)
```

The next stage is to then pull out the intersection layer, currently we only have a function
to plot the identified triangles - but work to come will identify them individually and copy attributes from the input layers appropriately. 

```{r}
plot(pool, col = "firebrick", show_intersection = TRUE)

## it works with pairs or with multiple layers
plot(polymer(A, B), col = "firebrick", show_intersection = TRUE)

plot(polymer(C, B), col = "firebrick", show_intersection = TRUE)


set.seed(sum(match(unlist(strsplit("polymer", "")), letters)))
## number of layers is arbitrary
plot(polymer(C, B, A, sf::st_jitter(A, 0.1)), col = "firebrick", show_intersection = TRUE)


```


A function `layer_n` will pull out any >=n overlaps. 

```{r nintersections}

plot(A["layer"], col = viridis::viridis(nrow(A)), reset = FALSE)
plot(B, add = TRUE, col = "hotpink")
plot(C, add = TRUE, col = "firebrick")
```
```{r}
plot(A["layer"], col = viridis::viridis(nrow(A)), reset = FALSE)
plot(B, add = TRUE, col = "hotpink")
plot(C, add = TRUE, col = "firebrick")

sb <- polymer(A, B, C)
plot(layer_n(sb), add = TRUE, col = "grey")
plot(layer_n(sb, n = 3), add = TRUE, col = "dodgerblue")


x <- layer_n(sb, n = 3)

## see how we know the identity of each input layer
tibble::as_tibble(x) %>%  dplyr::select(-geometry) %>% tidyr::unnest()
```

```{r so-example}
plot(soil, col = sf::sf.colors(n = nrow(soil)), border = NA, reset = FALSE)
plot(field, add = TRUE, col = NA)

soil_field <- polymer(soil, field)
plot(layer_n(soil_field), add = TRUE, border = rgb(0.5, 0.5, 0.5, 0.2))
```


From `vignette("over", package = "sp")`. 

```{r over}
 library(sp)
library(sf)
 x = c(0.5, 0.5, 1.0, 1.5)
 y = c(1.5, 0.5, 0.5, 0.5)
 xy = cbind(x,y)
 dimnames(xy)[[1]] = c("a", "b", "c", "d")
 pts = SpatialPoints(xy)
 xpol = c(0,1,1,0,0)
 ypol = c(0,0,1,1,0)
 pol = SpatialPolygons(list(
 Polygons(list(Polygon(cbind(xpol-1.05,ypol))), ID="x1"),
 Polygons(list(Polygon(cbind(xpol,ypol))), ID="x2"),
 Polygons(list(Polygon(cbind(xpol,ypol - 1.0))), ID="x3"),
 Polygons(list(Polygon(cbind(xpol + 1.0, ypol))), ID="x4"),
 Polygons(list(Polygon(cbind(xpol+.4, ypol+.1))), ID="x5")
))
pol <- st_as_sf(SpatialPolygonsDataFrame(disaggregate(pol), data.frame(a = 1:5)))
(polb <- polymer(pol[1, ], pol[2, ], pol[3, ], pol[4, ], pol[5, ]))
plot(polb, reset = FALSE)
plot(layer_n(polb), add = TRUE, col = rgb(0, 0, 0, 0.3), border = "firebrick", lwd = 2)
```

## Background details 

The resulting mesh and inputs and indexes can be used to derive complex
relationships between layers. polymer is modelled on the concept of **data
fusion** from a now defunct commercial package called Eonfusion. It relies on
the RTriangle package which is licensed CC BY-NC-SA 4.0, but could be modified
to use the less restrictive `decido` package. Specialist forms of this might
choose other engines - the crux is constrained triangulation, and for planar shapes high-quality triangles aren't required so long as all inputs edges are preserved. 

This is analogous to what GIS packages variously call "overlay", "topology
overlay", "intersection" and so on. The difference is we want a single mesh that
has information about all of its inputs in a lossless form. We can derive
general information from the mesh and the links to sources without simplifying
everything to a single result that has no connection to the sources.


---

Please note that the polymer project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/1/0/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
