---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# spacebucket

The goal of spacebucket is to provide flexible and intuitive overlay methods familiar 
to GIS workflows. This works by doing the obvious finite-element decomposition of all
component edges in all inputs into triangles. Then triangles *instances* are classified (by point-in-polygon lookup) by inclusion within paths within objects within layers. 

The resulting mesh and inputs and indexes can be used to derive complex relationships between
layers. Spacebucket is modelled on the concept of **data fusion** from a now defunct commercial package called Eonfusion. It relies on the RTriangle package which is licensed CC BY-NC-SA 4.0, but could be modified to use the less restrictive `decido` package. 

WIP

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mdsumner/spacebucket")
```

## Example

This example takes three built in data sets and merges them together as an indexed mesh. 

```{r example}
library(spacebucket)
plot(st_geometry(A), col = viridis::viridis(nrow(A)))
plot(st_geometry(B), col = "firebrick", add = TRUE)
plot(st_geometry(C), col = "dodgerblue", add = TRUE)

## summarize the contents
(bucket <- spacebucket(A, B, C))

## show the components pieces
plot(bucket, asp = 1)
```

The next stage is to then pull out the intersection layer, currently we only have a function
to plot the identified triangles - but work to come will identify them individually and copy attributes from the input layers appropriately. 

```{r}
spacebucket:::sb_intersection(bucket, col = "firebrick")

## it works with pairs or with multiple layers
spacebucket:::sb_intersection(spacebucket(A, B), col = "firebrick")

spacebucket:::sb_intersection(spacebucket(C, B), col = "firebrick")

## number of layers is arbitrary
spacebucket:::sb_intersection(spacebucket(C, B, A, st_jitter(A, 0.1)), col = "firebrick")


```


